\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-04-12 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex

\item [nummaterial\_velocity\_file] Defines the material properties.
\begin{itemize}
\item For classical materials (i.e., spectral elements for which the velocity and density
model will not be assigned by calling an external function to define for instance a tomographic model), the format is:
\begin{lyxcode}
\texttt{domain\_ID} \texttt{material\_ID}  \texttt{rho}  \texttt{vp}  \texttt{vs}  \texttt{Q}  \texttt{anisotropy\_flag}
\end{lyxcode}
where \textbf{\texttt{domain\_ID} is 1 for acoustic and 2 for elastic or viscoelastic materials,}
\texttt{material\_ID} a unique identifier,  \texttt{rho} the density in $kg \, m^{-3}$,  \texttt{vp} the P-wave speed in $m \, s^{-1}$, \texttt{vs}  the S-wave speed in $m \, s^{-1}$, \texttt{Q} the quality factor and \texttt{anisotropy\_flag} an identifier for anisotropic models.
%%magnoni
\item For tomographic velocity models, please read Chapter \ref{cha:-Changing-the} and Section \ref{sec:Using-tomographic} `Using external tomographic Earth models' for further details.
%
\end{itemize}

>>>>

\item [nummaterial\_velocity\_file] Defines the material properties.
\begin{itemize}
\item For classical materials (i.e., spectral elements for which the velocity and density
model will not be assigned by calling an external function to define for instance a tomographic model), the format is:
\begin{lyxcode}
\texttt{domain\_ID} \texttt{material\_ID}  \texttt{rho}  \texttt{vp}  \texttt{vs}  \texttt{Qkappa}  \texttt{Qmu} \texttt{anisotropy\_flag}
\end{lyxcode}
where \textbf{\texttt{domain\_ID} is 1 for acoustic and 2 for elastic or viscoelastic materials,}
\texttt{material\_ID} a unique identifier,  \texttt{rho} the density in $kg \, m^{-3}$,  \texttt{vp} the P-wave speed in $m \, s^{-1}$,
\texttt{vs}  the S-wave speed in $m \, s^{-1}$, \texttt{Q} the quality factor and \texttt{anisotropy\_flag} an identifier for anisotropic models.
Note that the \texttt{Qkappa} value is ignored by the code unless \texttt{FULL\_ATTENUATION\_SOLID} is set.
Note also that both \texttt{Qkappa} and \texttt{Qmu} are ignored by the code unless \texttt{ATTENUATION} is set.
If you want a model with no \texttt{Qmu} attenuation, both set \texttt{ATTENUATION} to \texttt{.false.} in the \texttt{Par\_file} and set \texttt{Qmu} to 9999 here.
If you want a model with no \texttt{Qkappa} attenuation, both set \texttt{FULL\_ATTENUATION\_SOLID} to \texttt{.false.} in the \texttt{Par\_file} and set \texttt{Qkappa} to 9999 here.
%%magnoni
\item For tomographic velocity models, please read Chapter \ref{cha:-Changing-the} and Section \ref{sec:Using-tomographic} `Using external tomographic Earth models' for further details.
%
\end{itemize}
